Stats

### 2022-08-10 stats/analysis.Rmd
adjust splithalfr calculation

```{r variation_hedge_plot}
hedge_variation_plot <- ggplot() +
  # child data
  geom_smooth(
    data = variationHedgeInd %>% filter(sample == "kids"),  
    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
    method = "lm", size = 0.5, alpha = 0.15, col = "darkgrey",
  ) +

  labs(x = "Age in years", y = "Average imprecision in target width", col = "Age group", shape = "Data collection mode", alpha = "Data collection mode", lty = "Data collection mode") + 
  scale_color_manual(values = c("#00b1ea", "#006c66", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) + 
  scale_x_continuous(breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) +

hedge_variation_plot

ggsave("../figures/gafo_hedge_variation.png", width = 7, height = 4)
```

@@

pp_check(mAgeHedge) + xlim(0, 10)
```

@@

hedge_variation_plot_GLMM

ggsave("../figures/gafo_hedge_variation_GLMM.png", width = 7, height = 4)
```

@@

```{r variation_box_plot}
# with remote sample
box_variation_plot <- ggplot() +
  # chance level
  geom_segment(aes(x = 3.0, y = 0.2, xend = 6.2, yend = 0.2), lty = "dotted") + 
  geom_segment(aes(x = 6.25, y = 0.125, xend = 6.75, yend = 0.125), lty = "dotted") +

  # child data
  geom_smooth(
    data = variationBoxInd %>% filter(sample == "kids"),  
    aes(x = ageInYearsExact, y = mean, group = datacollection, lty = datacollection), 
    method = "glm", size = 0.5, alpha = 0.15, col = "darkgrey",
  ) +

  # adult data
  geom_jitter(
    data = variationBoxInd %>% filter(sample == "adults"), 
    aes(x = 6.5, y = mean, col = ageInYears, shape = datacollection), alpha = 0.5, width = .05, height = .01,  
  ) +

box_variation_plot

ggsave("../figures/gafo_box_variation.png", width = 5, height = 4)
```

@@

ggsave("../figures/gafo_box_variation_GLMM.png", width = 7, height = 4)
```

@@

## Internal consistency
```{r intCon_hedge_data}
# take data of first reli day for internal consistency
hedge_intCon <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample, ageInYears) %>%
  tidyboot_mean(column = clickDistInBalloons, na.rm = TRUE)

@@

ggsave("../figures/gafo_hedge_intCon_kids.png", width = 6, height = 4)
```

@@

ggsave("../figures/gafo_hedge_intCon_adults.png", width = 6, height = 4)
```

@@

ggsave("../figures/gafo_box_intCon_kids.png", width = 6, height = 4)
```

@@

ggsave("../figures/gafo_box_intCon_adults.png", width = 6, height = 4)
```

```{r splithalfr_luke}
fn_score_hedge <- function(ds) {
  return(mean(ds$clickDistInBalloons, na.rm = TRUE))
}

@@

# random split
splitscores_hedge_random_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 25,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
)

hedge_random_kids <- split_coefs(splitscores_hedge_random_kids, cor)
uniq_reps <- unique(splitscores_hedge_random_kids$replication)

parallel_split_ci <- function(r) {
        return(split_ci(filter(splitscores_hedge_random_kids, replication==r), cor))
}

hedge_random_kids_ci <- mclapply(uniq_reps, parallel_split_ci, mc.cores=48)
# Darn R

# create dataframe to save data
splithalf_data <- tibble(
  studyversion = "hedge",
  sample = "kids",
  split = "random",
  stratification = "none",
  mean = hedge_random_kids)

splithalf_data$CI_lower = numeric(nrow(splithalf_data))
splithalf_data$CI_upper = numeric(nrow(splithalf_data))
for(i in 1:nrow(splithalf_data)) {
  splithalf_data$CI_lower[i] <- hedge_random_kids_ci[[i]]$lims["0.025","bca"]
  splithalf_data$CI_upper[i] <- hedge_random_kids_ci[[i]]$lims["0.975","bca"]
}

print(splithalf_data)
# write_csv(splithalf_data, "splithalf_data.csv")
```

```{r splithalfr_hedge_kids}
# fn_score_hedge <- function(ds) {
#   return(mean(ds$clickDistInBalloons, na.rm = TRUE))
# }
# 
# hedge_intCon_data <- reli %>% 
#   filter(studyversion == "hedge" & reliday == "reliday1")
# 
# # first-second half split
# splitscores_hedge_firstsecond_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("first_second"),
#   ncores = 1,
#   verbose = F
# )
# 
# hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
# hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)
# 
# splithalf_data <- tibble(
#                           sample = "kids", 
#                           studyversion = "hedge", 
#                           method = "first-second", 
#                           stratification = "none",                                        
#                           coefficient = hedge_firstsecond_kids, 
#                           CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
#                           CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
#                         )
# 
# # first-second half stratified by target position
# splitscores_hedge_firstsecondStrat_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("first_second"),
#   ncores = 1,
#   verbose = F, 
#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
# )
# 
# hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
# hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "first-second",
#                                         stratification = "target position",
#                                         coefficient = hedge_firstsecondStrat_kids,
#                                         CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # odd-even split
# splitscores_hedge_oddeven_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("odd_even"),
#   ncores = 1,
#   verbose = F
# )
# 
# hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
# hedge_oddeven_kids_ci <- split_ci(splitscores_hedge_oddeven_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "odd-even",
#                                         stratification = "none",
#                                         coefficient = hedge_oddeven_kids,
#                                         CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # odd-even split stratified by target position
# splitscores_hedge_oddevenStrat_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("odd_even"),
#   ncores = 1,
#   verbose = F, 
#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
# )
# 
# hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
# hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "odd-even",
#                                         stratification = "target position",
#                                         coefficient = hedge_oddevenStrat_kids,
#                                         CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # permutated splitting (random sampling without replacement)
# splitscores_hedge_permutated_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
# )
# 
# hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)
# hedge_permutated_kids_ci <- split_ci(splitscores_hedge_permutated_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "permutated",
#                                         stratification = "none",
#                                         coefficient = hedge_permutated_kids,
#                                         CI_lower = hedge_permutated_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_permutated_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # permutated splitting stratified by target position
# splitscores_hedge_permutatedStrat_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
# )
# 
# hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)
# hedge_permutatedStrat_kids_ci <- split_ci(splitscores_hedge_permutatedStrat_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "permutated",
#                                         stratification = "target position",
#                                         coefficient = hedge_permutatedStrat_kids,
#                                         CI_lower = hedge_permutatedStrat_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_permutatedStrat_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # monte carlo (sampling with replacement)
# splitscores_hedge_montecarlo_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
#   replace = TRUE,
# )
# 
# hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)
# hedge_montecarlo_kids_ci <- split_ci(splitscores_hedge_montecarlo_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "Monte Carlo",
#                                         stratification = "none",
#                                         coefficient = hedge_montecarlo_kids,
#                                         CI_lower = hedge_montecarlo_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_montecarlo_kids_ci$lims["0.975","bca"]
#                                       )
# 
# # monte carlo stratified by target position
# splitscores_hedge_montecarloStrat_kids <- by_split(
#   hedge_intCon_data %>% filter(sample == "kids"),
#   hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,
#   replace = TRUE,
#   stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
# )
# 
# hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)
# hedge_montecarloStrat_kids_ci <- split_ci(splitscores_hedge_montecarloStrat_kids, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "kids", 
#                                         studyversion = "hedge", 
#                                         method = "Monte Carlo",
#                                         stratification = "target position",
#                                         coefficient = hedge_montecarloStrat_kids,
#                                         CI_lower = hedge_montecarloStrat_kids_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_montecarloStrat_kids_ci$lims["0.975","bca"]
#                                       )
```

```{r splithalfr_hedge_adults}
# # first-second half split
# splitscores_hedge_firstsecond_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("first_second"),
#   ncores = 1,
#   verbose = F
# )
# 
# hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
# hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                               sample = "adults", 
#                                               studyversion = "hedge", 
#                                               method = "first-second", 
#                                               stratification = "none",                                        
#                                               coefficient = hedge_firstsecond_adults, 
#                                               CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
#                                               CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
#                                             )
# 
# # first-second half stratified by target position
# splitscores_hedge_firstsecondStrat_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("first_second"),
#   ncores = 1,
#   verbose = F, 
#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
# )
# 
# hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
# hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "adults", 
#                                         studyversion = "hedge", 
#                                         method = "first-second",
#                                         stratification = "target position",
#                                         coefficient = hedge_firstsecondStrat_adults,
#                                         CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
#                                       )
# 
# # odd-even split
# splitscores_hedge_oddeven_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("odd_even"),
#   ncores = 1,
#   verbose = F
# )
# 
# hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
# hedge_oddeven_adults_ci <- split_ci(splitscores_hedge_oddeven_adults, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "adults", 
#                                         studyversion = "hedge", 
#                                         method = "odd-even",
#                                         stratification = "none",
#                                         coefficient = hedge_oddeven_adults,
#                                         CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
#                                       )
# 
# # odd-even split stratified by target position
# splitscores_hedge_oddevenStrat_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("odd_even"),
#   ncores = 1,
#   verbose = F, 
#   stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
# )
# 
# hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
# hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)
# 
# splithalf_data <- splithalf_data %>% add_row(
#                                         sample = "adults", 
#                                         studyversion = "hedge", 
#                                         method = "odd-even",
#                                         stratification = "target position",
#                                         coefficient = hedge_oddevenStrat_adults,
#                                         CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
#                                         CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
#                                       )
# 
# # permutated splitting (random sampling without replacement)
# splitscores_hedge_permutated_adults <- by_split(
#   hedge_intCon_data %>% filter(sample == "adults"),
#   hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
#   fn_score_hedge,
#   method = c("random"),
#   ncores = 1,
#   verbose = F, 
#   replications = 1,

>>>>

@@

# pp_check(mAgeHedge) + xlim(0, 10)
```

@@

hedge_variation_plot_GLMM
saveRDS(hedge_variation_plot_GLMM, file = "../saves/gafo-hedge-variation-plot-GLMM.rds")
# ggsave("../figures/gafo_hedge_variation_GLMM.png", width = 7, height = 4)
```

@@

@@

saveRDS(box_variation_plot_GLMM, file = "../saves/gafo-box-variation-plot-GLMM.rds")
# ggsave("../figures/gafo_box_variation_GLMM.png", width = 7, height = 4)
```

@@

## Splithalf Reliability Data
```{r intCon_hedge_data}
# take data of first reli day for internal consistency
hedge_intCon <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample, ageInYears) %>%
  tidyboot_mean(column = clickDistInBalloons, na.rm = TRUE)

@@

saveRDS(hedge_intCon_kids, file = "../saves/gafo-hedge-intCon-kids.rds")
# ggsave("../figures/gafo_hedge_intCon_kids.png", width = 6, height = 4)
```

@@

saveRDS(hedge_intCon_adults, file = "../saves/gafo-hedge-intCon-adults.rds")
# ggsave("../figures/gafo_hedge_intCon_adults.png", width = 6, height = 4)
```

@@

saveRDS(box_intCon_kids, file = "../saves/gafo-box-intCon-kids.rds")
# ggsave("../figures/gafo_box_intCon_kids.png", width = 6, height = 4)
```

@@

saveRDS(box_intCon_adults, file = "../saves/gafo-box-intCon-adults.rds")
# ggsave("../figures/gafo_box_intCon_adults.png", width = 6, height = 4)
```

## Splithalf Reliability - Hedge Kids

```{r splithalfr_hedge_kids_firstsecond}
fn_score_hedge <- function(ds) {
  return(mean(ds$clickDistInBalloons, na.rm = TRUE))
}

@@

# first-second half split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F
)

hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)

splithalf_data <- tibble(
                          sample = "kids",
                          studyversion = "hedge",
                          method = "first-second",
                          stratification = "none",
                          coefficient = hedge_firstsecond_kids,
                          CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"],
                          CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
                        )

# first-second half stratified by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids",
                                        studyversion = "hedge",
                                        method = "first-second",
                                        stratification = "target position",
                                        coefficient = hedge_firstsecondStrat_kids,
                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"],
                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_hedge_kids_oddeven}
# odd-even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F
)

hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
hedge_oddeven_kids_ci <- split_ci(splitscores_hedge_oddeven_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids",
                                        studyversion = "hedge",
                                        method = "odd-even",
                                        stratification = "none",
                                        coefficient = hedge_oddeven_kids,
                                        CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"],
                                        CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
                                      )

# odd-even split stratified by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  method = c("odd_even"),
  ncores = 1,
  verbose = F,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids",
                                        studyversion = "hedge",
                                        method = "odd-even",
                                        stratification = "target position",
                                        coefficient = hedge_oddevenStrat_kids,
                                        CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"],
                                        CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_hedge_kids_permutated}
# permutated splitting (random sampling without replacement)
splitscores_hedge_permutated_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
)

hedge_permutated_kids <- split_coefs(splitscores_hedge_permutated_kids, cor)

splitscores_hedge_permutated_kids_uniq_reps <- unique(splitscores_hedge_permutated_kids$replication)

splitscores_hedge_permutated_kids_parallel_split_ci <- function(r) {
        return(split_ci(filter(splitscores_hedge_permutated_kids, replication==r), cor))
}

hedge_permutated_kids_ci <- mclapply(splitscores_hedge_permutated_kids_uniq_reps, splitscores_hedge_permutated_kids_parallel_split_ci, mc.cores=48)

hedge_permutated_kids_tbl <- tibble(
  studyversion = "hedge",
  sample = "kids",
  split = "permutated",
  stratification = "none",
  mean = hedge_permutated_kids)

hedge_permutated_kids_tbl$CI_lower = numeric(nrow(hedge_permutated_kids_tbl))
hedge_permutated_kids_tbl$CI_upper = numeric(nrow(hedge_permutated_kids_tbl))

for(i in 1:nrow(hedge_permutated_kids_tbl)) {
  hedge_permutated_kids_tbl$CI_lower[i] <- hedge_permutated_kids_ci[[i]]$lims["0.025","bca"]
  hedge_permutated_kids_tbl$CI_upper[i] <- hedge_permutated_kids_ci[[i]]$lims["0.975","bca"]
}

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids",
                                        studyversion = "hedge",
                                        method = "permutated",
                                        stratification = "none",
                                        coefficient = mean(hedge_permutated_kids_tbl$mean),
                                        CI_lower = mean(hedge_permutated_kids_tbl$CI_lower),
                                        CI_upper = mean(hedge_permutated_kids_tbl$CI_upper),
                                      )
```

```{r splithalfr_hedge_kids_permutated_stratified}
# permutated splitting stratified by target position
splitscores_hedge_permutatedStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_permutatedStrat_kids <- split_coefs(splitscores_hedge_permutatedStrat_kids, cor)

splitscores_hedge_permutatedStrat_kids_uniq_reps <- unique(splitscores_hedge_permutatedStrat_kids$replication)

splitscores_hedge_permutatedStrat_kids_parallel_split_ci <- function(r) {
        return(split_ci(filter(splitscores_hedge_permutatedStrat_kids, replication==r), cor))
}

hedge_permutatedStrat_kids_ci <- mclapply(splitscores_hedge_permutatedStrat_kids_uniq_reps, splitscores_hedge_permutatedStrat_kids_parallel_split_ci, mc.cores=48)

hedge_permutatedStrat_kids_tbl <- tibble(
  studyversion = "hedge",
  sample = "kids",
  split = "random",
  stratification = "target position",
  mean = hedge_permutatedStrat_kids)

hedge_permutatedStrat_kids_tbl$CI_lower = numeric(nrow(hedge_permutatedStrat_kids_tbl))
hedge_permutatedStrat_kids_tbl$CI_upper = numeric(nrow(hedge_permutatedStrat_kids_tbl))

for(i in 1:nrow(hedge_permutatedStrat_kids_tbl)) {
  hedge_permutatedStrat_kids_tbl$CI_lower[i] <- hedge_permutatedStrat_kids_ci[[i]]$lims["0.025","bca"]
  hedge_permutatedStrat_kids_tbl$CI_upper[i] <- hedge_permutatedStrat_kids_ci[[i]]$lims["0.975","bca"]
}

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids",
                                        studyversion = "hedge",
                                        method = "permutated",
                                        stratification = "target position",
                                        coefficient = mean(hedge_permutatedStrat_kids_tbl$mean),
                                        CI_lower = mean(hedge_permutatedStrat_kids_tbl$CI_lower),
                                        CI_upper = mean(hedge_permutatedStrat_kids_tbl$CI_upper),
                                      )
```

```{r splithalfr_hedge_kids_montecarlo}
# monte carlo (sampling with replacement)
splitscores_hedge_montecarlo_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
)

hedge_montecarlo_kids <- split_coefs(splitscores_hedge_montecarlo_kids, cor)

splitscores_hedge_montecarlo_kids_uniq_reps <- unique(splitscores_hedge_montecarlo_kids$replication)

splitscores_hedge_montecarlo_kids_parallel_split_ci <- function(r) {
        return(split_ci(filter(splitscores_hedge_montecarlo_kids, replication==r), cor))
}

hedge_montecarlo_kids_ci <- mclapply(splitscores_hedge_montecarlo_kids_uniq_reps, splitscores_hedge_montecarlo_kids_parallel_split_ci, mc.cores=48)

hedge_montecarlo_kids_tbl <- tibble(
  studyversion = "hedge",
  sample = "kids",
  split = "Monte Carlo",
  stratification = "none",
  mean = hedge_montecarlo_kids)

hedge_montecarlo_kids_tbl$CI_lower = numeric(nrow(hedge_montecarlo_kids_tbl))
hedge_montecarlo_kids_tbl$CI_upper = numeric(nrow(hedge_montecarlo_kids_tbl))

for(i in 1:nrow(hedge_montecarlo_kids_tbl)) {
  hedge_montecarlo_kids_tbl$CI_lower[i] <- hedge_montecarlo_kids_ci[[i]]$lims["0.025","bca"]
  hedge_montecarlo_kids_tbl$CI_upper[i] <- hedge_montecarlo_kids_ci[[i]]$lims["0.975","bca"]
}

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids",
                                        studyversion = "hedge",
                                        method = "Monte Carlo",
                                        stratification = "none",
                                        coefficient = mean(hedge_montecarlo_kids_tbl$mean),
                                        CI_lower = mean(hedge_montecarlo_kids_tbl$CI_lower),
                                        CI_upper = mean(hedge_montecarlo_kids_tbl$CI_upper),
                                      )
```

```{r splithalfr_hedge_kids_montecarlo_stratified}
# monte carlo stratified by target position
splitscores_hedge_montecarloStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 5000,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  ncores = 7, # setting ncores equally to something less than detectCores()
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricPosition),
)

hedge_montecarloStrat_kids <- split_coefs(splitscores_hedge_montecarloStrat_kids, cor)

splitscores_hedge_montecarloStrat_kids_uniq_reps <- unique(splitscores_hedge_montecarloStrat_kids$replication)

splitscores_hedge_montecarloStrat_kids_parallel_split_ci <- function(r) {
        return(split_ci(filter(splitscores_hedge_montecarloStrat_kids, replication==r), cor))
}

hedge_montecarloStrat_kids_ci <- mclapply(splitscores_hedge_montecarloStrat_kids_uniq_reps, splitscores_hedge_montecarloStrat_kids_parallel_split_ci, mc.cores=48)

hedge_montecarloStrat_kids_tbl <- tibble(
  studyversion = "hedge",
  sample = "kids",
  split = "Monte Carlo",
  stratification = "target position",
  mean = hedge_montecarloStrat_kids)

hedge_montecarloStrat_kids_tbl$CI_lower = numeric(nrow(hedge_montecarloStrat_kids_tbl))
hedge_montecarloStrat_kids_tbl$CI_upper = numeric(nrow(hedge_montecarloStrat_kids_tbl))

for(i in 1:nrow(hedge_montecarloStrat_kids_tbl)) {
  hedge_montecarloStrat_kids_tbl$CI_lower[i] <- hedge_montecarloStrat_kids_ci[[i]]$lims["0.025","bca"]
  hedge_montecarloStrat_kids_tbl$CI_upper[i] <- hedge_montecarloStrat_kids_ci[[i]]$lims["0.975","bca"]
}

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "kids",
                                        studyversion = "hedge",
                                        method = "Monte Carlo",
                                        stratification = "target position",
                                        coefficient = mean(hedge_montecarloStrat_kids_tbl$mean),
                                        CI_lower = mean(hedge_montecarloStrat_kids_tbl$CI_lower),
                                        CI_upper = mean(hedge_montecarloStrat_kids_tbl$CI_upper),
                                      )
```

####
## Splithalf Reliability - Hedge Adults

```{r splithalfr_hedge_adults_firstsecond}
# first-second half split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F
)

hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        sample = "adults",
                                        studyversion = "hedge",
                                        method = "first-second",
                                        stratification = "none",
                                        coefficient = hedge_firstsecond_adults,
                                        CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"],
                                        CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
                                      )

# first-second half stratified by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  method = c("first_second"),
  ncores = 1,
  verbose = F,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricPosition),
)

hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)
